Transferability of clinical prediction models for early trauma care

### 2019-08-23 ManuscriptMarkdown.Rmd
Exclude patients with missing date and time of trauma and report this number in the manuscript

## RESULTS
  ## Total patients and NA
  total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
  total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
  ## Sample NA
  na.vector <- unlist(results$NA.info.sample)
  names(na.vector) <- c("high volume", "high volume", "low volume", "low volume", "metropolitan", "metropolitan", "non metropolitan", "non metropolitan", "multi centre", "multi centre", "single centre", "single centre")
  highest.percent.missing.number <- max(na.vector[na.vector<100])
  highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
  ## Variable NA
  number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
  percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
  name.variable.na <- row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,])
  gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
  sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
  ## Development and validation
  ## Imputation data
  high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
  metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
  multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
  max.imp <- max(results$original.stats$Total.imputations)
  ## Validation data
  sorted.validation.mistriage <- sort(results.all.data[row.names(results.all.data) == "Validation.mistriage",], decreasing = FALSE)
  lowest.val.mistriage <- sorted.validation.mistriage[1]
  val.undertriage <- results.all.data["Validation.undertriage", colnames(lowest.val.mistriage)]
  val.overtriage <- results.all.data["Validation.overtriage", colnames(lowest.val.mistriage)]
  highest.val.mistriage <- sorted.validation.mistriage[6]
  ## Comparison
  ## Transfer data
  sorted.transfer.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transfer.mistriage",], decreasing = FALSE)
  lowest.tran.mistriage <- sorted.transfer.mistriage[1]
  highest.tran.mistriage <- sorted.transfer.mistriage[6]
  ## Comparison data
  sorted.comp.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transferred.mistriage.minus.buddy.local.mistriage",], decreasing = FALSE)
  highest.comp.mistriage <- sorted.comp.mistriage[6]
  worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]

@@

## Participants 
The eligibility criteria were adult patients aged 15 years or above registered 
in SweTrau between 2011 and 2016. The study aimed to assess adult trauma and not
paediatric trauma, which differs in physiology, triage and initial care
[@RN46]. The Swedish guidelines for trauma activation define children as 
individuals aged <15 years [@RN90].

@@

# Results
We analysed data from `r total.number.of.patients ` trauma patients to
investigate the effects of transfer on clinical prediction models (Table 1). The
total number of missing observations across all variables was `r total.number.of.na ` 
in the entire study cohort. The sample with the highest
percentage of missing observations was the `r highest.percent.missing.name `
sample, with `r highest.percent.missing.number `% incomplete observations. The
variable with the highest number of missing values was the `r name.variable.na `,
with `r number.variable.na ` missing values, or `r round(percent.variable.na)`% of 
the total values for this variable. The percentages of missing values for the other 
model predictors were `r round(gcs.na$percentage)`% for GCS and `r round(sbp.na$percentage)`% 
for SBP.

>>>>

## RESULTS
  ## Total patients and NA
  total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
  total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
  n.missing.data.time.of.trauma <- Results$n.missing.date.time.of.trauma
  ## Sample NA
  na.vector <- unlist(results$NA.info.sample)
  names(na.vector) <- c("high volume", "high volume", "low volume", "low volume", "metropolitan", "metropolitan", "non metropolitan", "non metropolitan", "multi centre", "multi centre", "single centre", "single centre")
  highest.percent.missing.number <- max(na.vector[na.vector<100])
  highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
  ## Variable NA
  number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
  percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
  name.variable.na <- row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,])
  gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
  sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
  ## Development and validation
  ## Imputation data
  high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
  metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
  multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
  max.imp <- max(results$original.stats$Total.imputations)
  ## Validation data
  sorted.validation.mistriage <- sort(results.all.data[row.names(results.all.data) == "Validation.mistriage",], decreasing = FALSE)
  lowest.val.mistriage <- sorted.validation.mistriage[1]
  val.undertriage <- results.all.data["Validation.undertriage", colnames(lowest.val.mistriage)]
  val.overtriage <- results.all.data["Validation.overtriage", colnames(lowest.val.mistriage)]
  highest.val.mistriage <- sorted.validation.mistriage[6]
  ## Comparison
  ## Transfer data
  sorted.transfer.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transfer.mistriage",], decreasing = FALSE)
  lowest.tran.mistriage <- sorted.transfer.mistriage[1]
  highest.tran.mistriage <- sorted.transfer.mistriage[6]
  ## Comparison data
  sorted.comp.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transferred.mistriage.minus.buddy.local.mistriage",], decreasing = FALSE)
  highest.comp.mistriage <- sorted.comp.mistriage[6]
  worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]

@@

## Participants 
The eligibility criteria were adult patients aged 15 years or above registered
in SweTrau between 2011 and 2016. The study aimed to assess adult trauma and not
paediatric trauma, which differs in physiology, triage and initial care
[@RN46]. The Swedish guidelines for trauma activation define children as
individuals aged <15 years [@RN90]. Further, patients with missing date and time
of trauma were excluded.

@@

# Results
We analysed data from `r total.number.of.patients ` trauma patients to
investigate the effects of transfer on clinical prediction models (Table 1), after 
excluding `r n.missing.date.time.of.trauma ` patients with missing date and time of 
trauma. The total number of missing observations across all variables was `r total.number.of.na ` 
in the entire study cohort. The sample with the highest
percentage of missing observations was the `r highest.percent.missing.name `
sample, with `r highest.percent.missing.number `% incomplete observations. The
variable with the highest number of missing values was the `r name.variable.na `,
with `r number.variable.na ` missing values, or `r round(percent.variable.na)`% of 
the total values for this variable. The percentages of missing values for the other 
model predictors were `r round(gcs.na$percentage)`% for GCS and `r round(sbp.na$percentage)`% 
for SBP.
